NHF1_FeatureRelativeFigureGeneration

### 2023-07-28 R/NHF1_FeatureRelativeFigureGeneration.Rmd
More changes to relation figure gen
- New x-axis cutoffs and labels.
- New periodicity analyses

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
mismatchTypes = list(`C>T_CC>TT` = NULL)
TFBSs = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL)
nucMaps = list(`hg19_mnase_all` = NULL)

@@

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
                                plotCountsMirror = TRUE, smoothCountsData = FALSE, mainYAxisLabel = "C>T Mismatches",
                                countsPlotColor = "black", countsMirrorColor = "gold2",
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))

      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"))

@@

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
                                plotCountsMirror = TRUE, smoothCountsData = FALSE, mainYAxisLabel = "C>T Mismatches",
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))

      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"))

@@

```{r periodicity analysis}
library(mutperiodR)

@@

>>>>

cellType = "NHF1"
CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
mismatchTypes = list(`C>T` = NULL, `CC>TT` = NULL, `C>T_CC>TT` = NULL)
TFBSs = list(`CTCF_known1_DHS` = NULL, `CTCF_known1_non-DHS` = NULL)
nucMaps = list(`hg19_mnase_all` = NULL)

@@

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
                                plotCountsMirror = TRUE, smoothCountsData = FALSE, mainYAxisLabel = "C>T Mismatches",
                                countsPlotColor = "black", countsMirrorColor = "gold2",
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"),
                                xAxisLabel = "TFBS-Relative Position")

      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, tfbs, "Aligned Strands"),
                                xAxisLabel = "TFBS-Relative Position")

@@

      plotFeatureRelativeCounts(featureRelativePositionData, FEATURE_RELATIVE_POSITION,
                                plotCountsMirror = TRUE, smoothCountsData = FALSE, mainYAxisLabel = "C>T Mismatches",
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"),
                                xAxisLabel = "Dyad-Relative Position", xlim = c(0,300))

      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"),
                                xAxisLabel = "Dyad-Relative Position", xlim = c(-100, 100))

      plotFeatureRelativeCounts(meanThreePrimeCutSiteDistanceData, FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                                smoothCountsData = FALSE, countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                                meanCutSiteDistanceTable = meanFivePrimeCutSiteDistanceData,
                                cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                                title = paste(cellType, "CPD", CPDTimepoint, mismatchType, nucMap, "Aligned Strands"),
                                xAxisLabel = "Dyad-Relative Position", xlim = c(0,300))

@@

```{r single_nucleosome_periodicity_analysis}
library(mutperiodR)

@@

```{r linker_region_periodicity_analysis}
library(mutperiodR)

        print("Mean 3` cut site distance:")
        print("  pre-linker:")
        periodAndSNR = getPeakPeriodicityAndSNR(
          meanThreePrimeCutSiteDistanceData[
            Feature_Relative_Mismatch_Pos < -70 & Feature_Relative_Mismatch_Pos > -120,
            Mean_Three_Prime_Cut_Site_Distance], 5, 25)
        print(paste("    Peak Period:",periodAndSNR[1]))
        print(paste("    SNR:",periodAndSNR[2]))

        print("  post-linker:")
        periodAndSNR = getPeakPeriodicityAndSNR(
          meanThreePrimeCutSiteDistanceData[
            Feature_Relative_Mismatch_Pos > 70 & Feature_Relative_Mismatch_Pos < 120,
            Mean_Three_Prime_Cut_Site_Distance], 5, 25)
        print(paste("    Peak Period:",periodAndSNR[1]))
        print(paste("    SNR:",periodAndSNR[2]))

        print("Mean 5` cut site distance:")
        print("  pre-linker:")
        periodAndSNR = getPeakPeriodicityAndSNR(
          meanFivePrimeCutSiteDistanceData[
            Feature_Relative_Mismatch_Pos < -70 & Feature_Relative_Mismatch_Pos > -120,
            Mean_Five_Prime_Cut_Site_Distance], 5, 25)
        print(paste("    Peak Period:",periodAndSNR[1]))
        print(paste("    SNR:",periodAndSNR[2]))

        print("  post-linker:")
        periodAndSNR = getPeakPeriodicityAndSNR(
          meanFivePrimeCutSiteDistanceData[
            Feature_Relative_Mismatch_Pos > 70 & Feature_Relative_Mismatch_Pos < 120,
            Mean_Five_Prime_Cut_Site_Distance], 5, 25)
        print(paste("    Peak Period:",periodAndSNR[1]))
        print(paste("    SNR:",periodAndSNR[2]))

        print('')
    }
  }
}
